%-------------------------
% Cover Letter in LaTeX (JOBKOMPASS JAKE TEMPLATE)
% Author : JobKompass
% Based on the Jake Resume Template style
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{parskip}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

% Set paragraph spacing
\setlength{\parindent}{0pt}
\setlength{\parskip}{10pt}

%-------------------------------------------
%%%%%%  COVER LETTER STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADER----------
\begin{center}
    \textbf{\Huge \scshape Itwela Ibomu} \\ \vspace{1pt}
    \small iibomu@wgu.edu $|$ Atlanta, GA
\end{center}

\vspace{20pt}

%----------DATE----------
January 18, 2026

\vspace{10pt}

%----------RECIPIENT----------
Hiring Manager\\
Whalar Group\\


\vspace{20pt}

%----------SALUTATION----------
Dear Hiring Manager,

\vspace{10pt}

%----------OPENING PARAGRAPH----------
I'm writing to apply for the Senior Machine Learning Engineer — Generative AI Applications role at Whalar Group. I build production-ready generative AI systems—agent pipelines, RAG/vector search, and multimodal generators—and I’d like to bring that experience to Whalar to help ship reliable, creative AI products.

%----------BODY PARAGRAPHS----------
Most recently I led development of Lotus, an iOS AI wellness app. I built an API-driven agent pipeline to orchestrate LLMs and multimodal generators for automated title, content, audio narration, and image generation while enforcing the company’s content and ethical guidelines. I produced audiobook narration used by my father, packaged audio + book bundles, and generated five-figure revenue from album and book sales. I also developed a monetization and pricing strategy by analyzing dozens of model cost/performance tradeoffs to ensure profitable unit economics.

Beyond Lotus, I’ve shipped production RAG/chat systems and customer-facing AI tools using LangChain/LangGraph, Pinecone, FastAPI, Docker, and TypeScript/Python stacks. My work focuses on scalable APIs, observability, and making cost-performance tradeoffs visible to product teams—skills I know Whalar values when moving models into production and building creative ML experiences.

%----------CLOSING PARAGRAPH----------
I’d welcome the chance to discuss how my hands-on experience with generative models, agent orchestration, and product-minded ML engineering can help Whalar build reliable, creative AI. Thank you for considering my application—my resume is attached and I’m available for a conversation at your convenience.

\vspace{20pt}

%----------SIGNATURE----------
Sincerely,

\vspace{40pt}

Itwela Ibomu

%-------------------------------------------
\end{document}

