\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{lmodern}  % Latin Modern fonts for better coverage
\usepackage[T1]{fontenc}  % Use T1 encoding for better font support
\usepackage{latexsym}
\usepackage{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{babel}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage[pdftex]{bookmark}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting - REDUCED SPACING
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-2pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}

\newcommand{\resumeFlexContent}[2]{
  \noindent\begin{minipage}[t]{0.2\textwidth}
    \textbf{#1}
  \end{minipage}%
  \hfill % This creates the space-between effect
  \begin{minipage}[t]{0.75\textwidth}
    \raggedright #2
  \end{minipage}\\[4pt]
}

% REDUCED SPACING in resumeSubheading
\newcommand{\resumeSubheading}[4]{\vspace{-4pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-5pt}}

% Modified to handle long technology lists with a comma-separated inline format
\newcommand{\resumeProjectHeading}[2]{\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & \small#2 \\
  \end{tabular*}\vspace{-5pt}}

\newcommand{\resumeProjectHeader}[2]{
  \vspace{-2pt}
  \item[]
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectDetails}[1]{
  \vspace{3pt}
  \begin{minipage}[t]{0.97\textwidth}
    \small #1
  \end{minipage}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% Set global paragraph spacing to minimum
\setlength{\parskip}{0pt}

% Set global paragraph spacing to minimum
\setlength{\parskip}{0pt}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setlength{\parskip}{0pt}
\begin{document}

\begin{center}
  \textbf{\Huge \scshape Itwela Ibomu} \\ \vspace{1pt}
  \small \href{mailto:Iibomu@wgu.edu}{\underline{Iibomu@wgu.edu}} $|$
  
  Salt Lake City, UT, USA $|$
  
  \href{https://github.com/itwela}{\underline{github.com/itwela}} $|$
  \href{https://itwela.dev}{\underline{itwela.dev}}
\end{center}
%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
           
             \resumeSubheading
               {Western Governors University (WGU)}{Salt Lake City, UT}
               {Bachelor of Science in Software Engineering}{Estimated Graduation: Expected Dec 2025}
               \resumeItemListStart
                 \resumeItem{Relevant coursework: Mathematics, Programming, Data Management, Application Design.}
          \resumeItem{Maintained strong academic performance across core engineering courses.}
               \resumeItemListEnd
           
           \resumeSubHeadingListEnd
%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
           
             \resumeSubheading
               {Headstarter}{Long Island City, NY}
               {Software Engineering Fellow}{Jul 2024 – Sep 2024}
               \resumeItemListStart
                 \resumeItem{Built and deployed 5 full‑stack AI web applications using React (TypeScript), Next.js, Tailwind, Firebase, Supabase, Clerk, LangChain, Pinecone, Docker, and Vercel.}
          \resumeItem{Scaled multiple web apps to 200+ users by iterating on product feedback, improving performance, and refining UX.}
          \resumeItem{Won two hackathons (including CitySwipe) and secured follow‑on interest/funding by demonstrating product-market fit and growth potential.}
               \resumeItemListEnd
           

             \resumeSubheading
               {Dataforce}{Atlanta, GA}
               {AI Software Engineer}{Apr 2024 – Jun 2024}
               \resumeItemListStart
                 \resumeItem{Improved captioning pipeline efficiency by 20\% through workflow optimization and automation, increasing throughput and client satisfaction.}
          \resumeItem{Diagnosed and fixed multiple production issues, reducing turnaround time and improving delivery reliability.}
          \resumeItem{Documented technical processes and implemented best practices to standardize caption production across projects.}
               \resumeItemListEnd
           

             \resumeSubheading
               {Forage (J.P. Morgan virtual experience)}{Remote}
               {Software Engineering Virtual Experience}{Dec 2023 – Jan 2024}
               \resumeItemListStart
                 \resumeItem{Implemented live graph generation using JPMorgan Chase’s open-source Perspective library; configured dev environment and resolved integration issues.}
          \resumeItem{Completed assigned engineering tasks ahead of schedule and validated outputs against provided datasets.}
               \resumeItemListEnd
           
           \resumeSubHeadingListEnd
%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
     
       \resumeProjectHeader
         {CitySwipe (AI Travel \& Vacation Planning)}{Jul 2024 – Present}
       
       \resumeProjectDetails{AI-powered vacation planning web app that recommends trip itineraries and bookings.}
       \resumeItem{Technologies Used: Next.js, React, Vercel, Supabase, Gemini}
       \resumeItemListStart
           \resumeItem{Led development and product strategy; grew the platform to 50+ users and generated thousands of social impressions.}
          \resumeItem{Secured investment interest from external stakeholders by pitching product growth and monetization plans.}
         \resumeItemListEnd
     

       \resumeProjectHeader
         {Job Tracker \& Data Analysis}{Jan 2024 – Apr 2024}
       
       \resumeProjectDetails{Job application tracker with automation and analytics to shorten application time.}
       \resumeItem{Technologies Used: Next.js, TypeScript, PostgreSQL}
       \resumeItemListStart
           \resumeItem{Reduced average job application time by 50\% by building automation and streamlined UI for tracking applications.}
         \resumeItemListEnd
     

       \resumeProjectHeader
         {RAG Rate My Professor Chat (MyJobKompass.com)}{Aug 2024}
       
       \resumeProjectDetails{Retrieval-Augmented Generation chat app with real-time data fetching and vector search.}
       \resumeItem{Technologies Used: Next.js, React, OpenAI, Pinecone, PostgreSQL}
       \resumeItemListStart
           \resumeItem{Implemented vector search and real-time data sync to improve response accuracy and user experience; served 10+ users.}
         \resumeItemListEnd
     

       \resumeProjectHeader
         {Jelly Up! — Instant Video Caption Generator}{Aug 2024}
       
       \resumeProjectDetails{Backend-driven video transcription and captioning system.}
       \resumeItem{Technologies Used: Next.js, React, Docker, OpenCV, OpenAI Whisper}
       \resumeItemListStart
           \resumeItem{Built a scalable pipeline for automated video captioning; achieved high transcription accuracy and productionized captioned videos.}
          \resumeItem{Placed 2nd at the Headstarter Hiring Hackathon among hundreds of teams.}
         \resumeItemListEnd
     

       \resumeProjectHeader
         {Globetrotter AI — Voice‑Activated Travel Assistant}{Aug 2024}
       
       \resumeProjectDetails{Voice-first travel assistant integrating multiple travel APIs.}
       \resumeItem{Technologies Used: Flask, APIs}
       \resumeItemListStart
           \resumeItem{Designed full-stack voice assistant and integrated third-party APIs; project won 1st place at a Headstarter Hiring Hackathon.}
         \resumeItemListEnd
     
     \resumeSubHeadingListEnd
%-----------TECHNICAL SKILLS-----------
\section{Skills}
\resumeFlexContent{Technical:}{Languages: Python, JavaScript/TypeScript, Frameworks: React, Next.js, React Native, Flask, Databases: PostgreSQL, Supabase, Firebase, Tools: Docker, Vercel, Clerk, OpenAI, LangChain, Pinecone, OpenAI Whisper, Other: OpenCV, Git, CI/CD}
        \resumeFlexContent{Additional:}{UI/UX Design, Leadership, Agile methodologies, Mentoring \& Teaching, Teamwork}
%-----------ADDITIONAL INFO-----------
\section{Additional Information}
\resumeFlexContent{Interests:}{Mentoring, Investing, Crypto, Basketball, Gaming, Traveling, Teaching}
        \resumeFlexContent{Hobbies:}{Piano, Guitar, Art}
        \resumeFlexContent{Languages:}{English (native)}
        \resumeFlexContent{References:}{Available upon request}
\end{document}