\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{lmodern}  % Latin Modern fonts for better coverage
\usepackage[T1]{fontenc}  % Use T1 encoding for better font support
\usepackage{latexsym}
\usepackage{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{babel}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage[pdftex]{bookmark}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting - REDUCED SPACING
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-2pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}

\newcommand{\resumeFlexContent}[2]{
  \noindent\begin{minipage}[t]{0.2\textwidth}
    \textbf{#1}
  \end{minipage}%
  \hfill % This creates the space-between effect
  \begin{minipage}[t]{0.75\textwidth}
    \raggedright #2
  \end{minipage}\\[4pt]
}

% REDUCED SPACING in resumeSubheading
\newcommand{\resumeSubheading}[4]{\vspace{-4pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-5pt}}

% Modified to handle long technology lists with a comma-separated inline format
\newcommand{\resumeProjectHeading}[2]{\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & \small#2 \\
  \end{tabular*}\vspace{-5pt}}

\newcommand{\resumeProjectHeader}[2]{
  \vspace{-2pt}
  \item[]
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectDetails}[1]{
  \vspace{3pt}
  \begin{minipage}[t]{0.97\textwidth}
    \small #1
  \end{minipage}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% Set global paragraph spacing to minimum
\setlength{\parskip}{0pt}

% Set global paragraph spacing to minimum
\setlength{\parskip}{0pt}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setlength{\parskip}{0pt}
\begin{document}

\begin{center}
  \textbf{\Huge \scshape Itwela Ibomu} \\ \vspace{1pt}
  \small \href{mailto:Iibomu@wgu.edu}{\underline{Iibomu@wgu.edu}} $|$
  
  Salt Lake City, UT $|$
  
  \href{https://github.com/itwela}{\underline{github.com/itwela}} $|$
  \href{https://itwela.dev}{\underline{itwela.dev}}
\end{center}
%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
           
             \resumeSubheading
               {Western Governors University (WGU)}{Salt Lake City, UT}
               {Bachelor of Science in Software Engineering}{Estimated Graduation: Expected December 2025}
               \resumeItemListStart
                 \resumeItem{Relevant coursework: Mathematics, Programming, Data Management, Application Design.}
          \resumeItem{Gained practical experience in software architecture, databases, and full-stack development through project-based learning.}
               \resumeItemListEnd
           
           \resumeSubHeadingListEnd
%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
           
             \resumeSubheading
               {Headstarter}{Long Island City, NY}
               {Software Engineering Fellow}{Jul 2024 - Sep 2024}
               \resumeItemListStart
                 \resumeItem{Built and deployed 5 AI-powered web applications using React (TypeScript), Next.js, Tailwind CSS, Firebase, Supabase, Clerk, LangChain, Pinecone, Docker, and Vercel.}
          \resumeItem{Scaled multiple web apps to 200+ users by iterating on user feedback, improving UX, and optimizing performance.}
          \resumeItem{Led development of 'CitySwipe'—an AI travel/vacation planning platform—securing funding and winning multiple hackathons.}
               \resumeItemListEnd
           

             \resumeSubheading
               {Dataforce}{Atlanta, GA}
               {AI Software Engineer}{Apr 2024 - Jun 2024}
               \resumeItemListStart
                 \resumeItem{Improved captioning project efficiency and productivity by ~20\% through workflow optimization and automation.}
          \resumeItem{Resolved technical issues and documented fixes, reducing cycle time and improving on-time delivery for client projects.}
          \resumeItem{Supported client satisfaction by consistently exceeding captioning targets and quality benchmarks.}
               \resumeItemListEnd
           

             \resumeSubheading
               {Forage (J.P. Morgan virtual experience)}{Remote}
               {Software Engineering Virtual Experience}{Dec 2023 - Jan 2024}
               \resumeItemListStart
                 \resumeItem{Set up development environment and implemented live graph generation using JPMorgan Chase’s open-source Perspective library.}
          \resumeItem{Diagnosed and fixed code issues to complete assigned tasks and demonstrate working data-visualization features.}
               \resumeItemListEnd
           
           \resumeSubHeadingListEnd
%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
     
       \resumeProjectHeader
         {CitySwipe (AI Travel \& Vacation Planning)}{Jul 2024 - Present}
       
       \resumeProjectDetails{AI-powered vacation planning platform that recommends itineraries and bookings based on user preferences.}
       \resumeItem{Technologies Used: Next.js, React, Vercel, Supabase, Gemini}
       \resumeItemListStart
           \resumeItem{Led a small team to build and launch the product; grew to 50+ active users and generated thousands of social impressions.}
          \resumeItem{Secured investment from Nabeel (CEO of Lunchbox) after pitching CitySwipe’s growth metrics and roadmap.}
         \resumeItemListEnd
     

       \resumeProjectHeader
         {Job Tracker \& Data Analysis Application}{Jan 2024 - Apr 2024}
       
       \resumeProjectDetails{Tool to track job applications and analyze pipeline metrics to reduce application time.}
       \resumeItem{Technologies Used: Next.js, TypeScript, PostgreSQL}
       \resumeItemListStart
           \resumeItem{Reduced average job application time by ~50\% via automation and streamlined tracking features.}
         \resumeItemListEnd
     

       \resumeProjectHeader
         {RAG AI Rate My Professor Chat Application}{Aug 2024}
       
       \resumeProjectDetails{Real-time chat interface using retrieval-augmented generation (RAG) for professor reviews and ratings.}
       \resumeItem{Technologies Used: Next.js, TypeScript, Pinecone, OpenAI}
       \resumeItemListStart
           \resumeItem{Built real-time data fetching and vector search to improve answer accuracy and user experience.}
         \resumeItemListEnd
     

       \resumeProjectHeader
         {MyJobKompass.com}{2024}
       
       \resumeProjectDetails{Job search assistant and personal dashboard for tracking applications and tips.}
       \resumeItem{Technologies Used: Next.js, React, OpenAI, PostgreSQL}
       \resumeItemListStart
           \resumeItem{Launched MVP with 10+ users; integrated AI-driven assistance to provide tailored job-hunting suggestions.}
         \resumeItemListEnd
     

       \resumeProjectHeader
         {Instant Video Caption Generator (Jelly Up!)}{Aug 2024}
       
       \resumeProjectDetails{Backend system for automated video transcription and caption embedding.}
       \resumeItem{Technologies Used: Next.js, React, Docker, OpenCV, OpenAI Whisper}
       \resumeItemListStart
           \resumeItem{Developed transcription pipeline and captioning system to generate accurate captioned videos.}
          \resumeItem{Placed 2nd in the Headstarter Hiring Hackathon among hundreds of teams.}
         \resumeItemListEnd
     

       \resumeProjectHeader
         {Globetrotter AI (Voice-Activated Travel Assistant)}{Aug 2024}
       
       \resumeProjectDetails{Voice-activated AI assistant that integrates travel APIs to provide personalized trip recommendations.}
       \resumeItem{Technologies Used: Flask, REST APIs, OpenAI}
       \resumeItemListStart
           \resumeItem{Designed full-stack solution with voice input, API orchestration, and contextual responses.}
          \resumeItem{Won 1st place in the Headstarter Hiring Hackathon.}
         \resumeItemListEnd
     
     \resumeSubHeadingListEnd
%-----------TECHNICAL SKILLS-----------
\section{Skills}
\resumeFlexContent{Technical:}{Python, JavaScript (TypeScript), React, Next.js, Node.js, React Native, PostgreSQL, Supabase, Firebase, Docker, OpenAI / LLMs, Pinecone, LangChain, OpenCV}
        \resumeFlexContent{Additional:}{UI/UX Design, Leadership, Agile, Team Collaboration, Problem Solving, Mentoring}
%-----------ADDITIONAL INFO-----------
\section{Additional Information}
\resumeFlexContent{Interests:}{Mentoring, Investing, Crypto, Basketball, Gaming, Traveling, Teaching}
        \resumeFlexContent{Hobbies:}{Piano, Guitar, Digital Art}
        \resumeFlexContent{Languages:}{English}
        
\end{document}