%-------------------------
% Resume in Latex (JOBKOMPASS JAKE TEMPLATE)
% Author : JobKompass
% Based off of: https://github.com/sb2nov/resume
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://YOUR-PORTFOLIO.com/}{\Large YOUR NAME}} & Email : \href{mailto:your.email@example.com}{your.email@example.com}\\
%   \href{http://YOUR-PORTFOLIO.com/}{http://YOUR-PORTFOLIO.com} & Mobile : YOUR-PHONE-NUMBER \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Itwela Ibomu} \\ \vspace{1pt}
    \small \underline{US Citizen} $|$ \href{mailto:iibomu@wgu.edu}{\underline{iibomu@wgu.edu}} $|$ \href{https://linkedin.com/in/linkedin.com/in/itwela}{\underline{linkedin.com/in/linkedin.com/in/itwela}} $|$ \href{https://github.com/github.com/itwela}{\underline{github.com/github.com/itwela}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Western Governors University (WGU)}{Salt Lake City, UT}
      {B.S. in Software Engineering}{December 2026 (Estimated)}
    \resumeItemListStart
      \resumeItem{Relevant coursework: Data Structures \& Algorithms; Python; Front-End Web Development; JavaScript}
    \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Software Engineer}{Jul 2025 - Dec 2025}
      {Dope Marketing}{Remote (HQ: Minnesota)}
    \resumeItemListStart
      \resumeItem{Built internal AI platform and production APIs that automated account research and data analysis for managers, reducing manual lookup time from hours to minutes.}
      \resumeItem{Designed and deployed APIs enabling agent access to millions of housing and client records, improving decision speed for leadership teams.}
      \resumeItem{Delivered three production tools adopted by management, improving research efficiency and enabling scalable automation.}
    \resumeItemListEnd
    \resumeSubheading
      {Software Engineering Fellow (AI/LLM Projects)}{Jul 2024 - Sep 2024}
      {Headstarter}{Remote (HQ: San Francisco, CA)}
    \resumeItemListStart
      \resumeItem{Led a team of 3 to design and ship CitySwipe, an LLM-powered travel planner (Next.js, LangChain, Pinecone, Supabase) that reached 200+ users and 50K+ impressions.}
      \resumeItem{Built and scaled five AI web apps using Next.js and LangChain; focused on RAG flows, vector search integration, and prompt engineering to improve relevance.}
      \resumeItem{Won 1st place out of 300+ teams in a nationwide hackathon for product innovation and execution.}
    \resumeItemListEnd
    \resumeSubheading
      {AI Engineer}{Apr 2024 - Jun 2024}
      {Dataforce}{Atlanta, GA}
    \resumeItemListStart
      \resumeItem{Improved automated video captioning pipeline using Whisper and OpenCV, reducing captioning error rates by 20\% across 200 videos/day.}
      \resumeItem{Implemented workflow automation and QA checks that increased processing consistency and deployment reliability.}
      \resumeItem{Built reproducible deployments (Docker) for media processing pipelines and provided operational documentation for handoffs.}
    \resumeItemListEnd
    \resumeSubheading
      {Software Intern}{}
      {J.P. Morgan (Forage)}{Remote}
    \resumeItemListStart
      \resumeItem{Implemented a real-time data visualization tool with <200ms updates using the Perspective library, gaining exposure to enterprise-scale data systems.}
      \resumeItem{Contributed to performance tuning and front-end data integration for high-frequency dashboards.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd
    %-------------------------------------------

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Lotus — AI Wellness App} $|$ \emph{React Native, Convex, OpenAI, Replicate, App Store deployment}}{}
    \resumeItemListStart
      \resumeItem{}
      \resumeItem{Built an API-driven agent pipeline to orchestrate LLMs and multimodal generators for automated title, content, audio narration, and image generation while enforcing the company’s content and ethical guidelines.}
      \resumeItem{Produced audiobook narration used by my father; packaged audio + book bundles and generated five-figure revenue from album and book sales.}
      \resumeItem{Developed a monetization and pricing strategy by analyzing dozens of model cost/performance tradeoffs to ensure profitable unit economics.}
    \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{CitySwipe — AI Travel Planner} $|$ \emph{Next.js, LangChain, Pinecone, Supabase}}{}
    \resumeItemListStart
      \resumeItem{Personalized travel recommendations using LLMs and vector search to produce context-aware suggestions and itineraries.}
      \resumeItem{Designed personalized recommendation flows using LangChain and vector search (Pinecone) to deliver context-aware suggestions.}
      \resumeItem{Iterated on prompt templates and UX to increase engagement to 200+ users and 50K+ impressions.}
    \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{RAG — Real-time Contextual Chat} $|$ \emph{Next.js, TypeScript, Pinecone, OpenAI}}{}
    \resumeItemListStart
      \resumeItem{Real-time RAG chat application using vector search to serve contextual answers and improve perceived relevance.}
      \resumeItem{Implemented vector-search retrieval-augmented generation architecture and TypeScript-first frontend/back-end glue for fast iteration and caching.}
      \resumeItem{Focused on evaluation and prompt tuning to improve response relevance.}
    \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{Globetrotter AI — Voice Travel Assistant} $|$ \emph{Flask, Python, OpenAI, Google TTS, React Three Fiber}}{}
    \resumeItemListStart
      \resumeItem{Voice-activated travel planner integrating speech recognition, LLM planning, and travel APIs to produce spoken itineraries.}
      \resumeItem{Built voice UX and multi-step agent planning flows using LLMs; integrated speech recognition and third-party travel APIs for end-to-end demos.}
      \resumeItem{Won 1st place at Headstarter Hiring Hackathon for voice UX, API integrations, and production-ready demo.}
    \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{Jelly Up! — Instant Video Caption Generator} $|$ \emph{Next.js, Whisper, OpenCV, Docker, FFmpeg}}{}
    \resumeItemListStart
      \resumeItem{Automated subtitles and burned-in captions using Whisper and OpenCV, deployed with Docker for reproducible demos.}
      \resumeItem{Architected an end-to-end automated captioning pipeline producing SRT and burned-in captions; improved caption sync via frame alignment heuristics.}
      \resumeItem{Placed 2nd at Headstarter Hiring Hackathon for technical execution and demo reliability.}
    \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{Job Tracker \& Analytics Dashboard} $|$ \emph{Next.js, PostgreSQL, Supabase}}{}
    \resumeItemListStart
      \resumeItem{Automated job tracking workflow and analytics dashboard.}
      \resumeItem{Built an automated job-tracking and analytics dashboard that reduced job application bookkeeping time by 50\% through workflow automation and templated application generation.}
      \resumeItem{Implemented robust serverless cron jobs and reporting to surface high-value follow-ups and status trends.}
    \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
        \textbf{Languages}{: Python, TypeScript, JavaScript, React, Next.js, React Native, Node.js, PostgreSQL, Supabase, Firebase, Docker, Pinecone, LangChain, Prompt engineering, Agent orchestration, RAG / Retrieval-Augmented Generation, Vector search (Pinecone), OpenAI, Convex, Replicate, App Store deployment, API design \& integration, Audio production \& publishing, Monetization \& pricing strategy, CI/CD concepts, Cloud fundamentals (AWS/GCP concepts)} \\
        \textbf{Additional Skills}{: UI/UX Design, Product Development, Agile, Leadership, Product analytics}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}