\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{lmodern}  % Latin Modern fonts for better coverage
\usepackage[T1]{fontenc}  % Use T1 encoding for better font support
\usepackage{latexsym}
\usepackage{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{babel}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage[pdftex]{bookmark}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting - REDUCED SPACING
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-2pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}

\newcommand{\resumeFlexContent}[2]{
  \noindent\begin{minipage}[t]{0.2\textwidth}
    \textbf{#1}
  \end{minipage}%
  \hfill % This creates the space-between effect
  \begin{minipage}[t]{0.75\textwidth}
    \raggedright #2
  \end{minipage}\\[4pt]
}

% REDUCED SPACING in resumeSubheading
\newcommand{\resumeSubheading}[4]{\vspace{-4pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-5pt}}

% Modified to handle long technology lists with a comma-separated inline format
\newcommand{\resumeProjectHeading}[2]{\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & \small#2 \\
  \end{tabular*}\vspace{-5pt}}

\newcommand{\resumeProjectHeader}[2]{
  \vspace{-2pt}
  \item[]
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectDetails}[1]{
  \vspace{3pt}
  \begin{minipage}[t]{0.97\textwidth}
    \small #1
  \end{minipage}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% Set global paragraph spacing to minimum
\setlength{\parskip}{0pt}

% Set global paragraph spacing to minimum
\setlength{\parskip}{0pt}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setlength{\parskip}{0pt}
\begin{document}

\begin{center}
  \textbf{\Huge \scshape Itwela Ibomu} \\ \vspace{1pt}
  \small \href{mailto:Iibomu@wgu.edu}{\underline{Iibomu@wgu.edu}} $|$
  (555) 123-4567 $|$
  Salt Lake City, UT $|$
  \href{https://linkedin.com/in/itwela-ibomu}{\underline{linkedin.com/in/itwela-ibomu}} $|$
  \href{https://github.com/itwela}{\underline{github.com/itwela}} $|$
  \href{https://itwela.dev}{\underline{itwela.dev}}
\end{center}
%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
           
             \resumeSubheading
               {Western Governors University (WGU)}{Salt Lake City, UT}
               {Bachelor of Science in Software Engineering }{Estimated Graduation: Expected Dec 2025}
               \resumeItemListStart
                 \resumeItem{Accomplished knowledge of Math, Programming, Data Management, and Application Design through in‑depth coursework and projects.}
               \resumeItemListEnd
           
           \resumeSubHeadingListEnd
%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
           
             \resumeSubheading
               {DOPE Marketing}{Remote / Salt Lake City, UT}
               {Software Engineer}{Jul 2025 - Present}
               \resumeItemListStart
                 \resumeItem{Full‑time software engineer contributing to the core product stack (Next.js, React, TypeScript, Node.js) and shipping customer‑facing features end‑to‑end.}
          \resumeItem{Implemented new onboarding flows, A/B test frameworks, and analytics instrumentation that improved feature rollout speed and visibility.}
          \resumeItem{Built and maintained CI/CD pipelines with Docker and Vercel, reducing deployment time and manual steps.}
          \resumeItem{Collaborated closely with product, design, and marketing to prioritize roadmap items and mentor junior engineers.}
               \resumeItemListEnd
           

             \resumeSubheading
               {Headstarter}{Long Island City, NY}
               {Software Engineering Fellow}{Jul 2024 - Sep 2024}
               \resumeItemListStart
                 \resumeItem{Built and deployed 5 AI projects using React (TypeScript), Next.js, Tailwind, Firebase, Supabase, Clerk, LangChain, Pinecone, Docker, and Vercel.}
          \resumeItem{Scaled web apps to 200+ users by iterating on user feedback and implementing frontend and backend optimizations.}
          \resumeItem{Led development of the CitySwipe project which won multiple hackathons and secured early investment.}
               \resumeItemListEnd
           

             \resumeSubheading
               {Dataforce}{Atlanta, GA}
               {AI Software Engineer}{Apr 2024 - Jun 2024}
               \resumeItemListStart
                 \resumeItem{Improved captioning project efficiency by ~20\% through workflow and tooling optimizations, increasing client satisfaction.}
          \resumeItem{Diagnosed and resolved technical issues across the captioning pipeline, reducing turnaround time for deliverables.}
          \resumeItem{Documented fixes and created reproducible bug reports to speed future troubleshooting.}
               \resumeItemListEnd
           

             \resumeSubheading
               {Forage (J.P. Morgan)}{Remote}
               {Software Engineering Virtual Experience}{Dec 2023 - Jan 2024}
               \resumeItemListStart
                 \resumeItem{Set up the development environment and fixed files to generate live graphs using J.P. Morgan Chase’s open‑source Perspective library.}
          \resumeItem{Delivered a working prototype for live graph generation as part of a team exercise.}
               \resumeItemListEnd
           
           \resumeSubHeadingListEnd
%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
     
       \resumeProjectHeader
         {CitySwipe (AI Travel \& Vacation Planning)}{Jul 2024 - Present}
       
       \resumeProjectDetails{AI‑powered vacation platform that recommends personalized itineraries and travel options.}
       \resumeItem{Technologies Used: Next.js, React, Vercel, Supabase, Gemini, TypeScript}
       \resumeItemListStart
           \resumeItem{Led the team and growth efforts; acquired 50+ active users and secured social impressions and early investor interest.}
          \resumeItem{Pitched to investors and secured a commitment from an early investor.}
         \resumeItemListEnd
     

       \resumeProjectHeader
         {Lotus Always Growing (iOS)}{Jun 2025}
       
       \resumeProjectDetails{Published iOS app available on the App Store focused on personal growth and habit tracking.}
       \resumeItem{Technologies Used: React Native, TypeScript, Expo}
       \resumeItemListStart
           \resumeItem{Designed, built, and published the app to the Apple App Store end‑to‑end.}
          \resumeItem{Handled feature development, bug fixes, and App Store submission process.}
         \resumeItemListEnd
     

       \resumeProjectHeader
         {Algorithmic Trading System}{May 2025}
       
       \resumeProjectDetails{Automated trading bot and risk management system used to pass a proprietary trading combine.}
       \resumeItem{Technologies Used: Python, Pandas, NumPy, Broker API integrations}
       \resumeItemListStart
           \resumeItem{Designed and implemented automated trading strategies and execution logic.}
          \resumeItem{Passed a trading combine and generated approximately \$14,000 in profit over a ~45‑day period.}
         \resumeItemListEnd
     

       \resumeProjectHeader
         {MyJobKompass.com (Job Tracker \& Data Analysis)}{Jan 2024 - Apr 2024}
       
       \resumeProjectDetails{Job application tracker and analytics dashboard to speed application workflows.}
       \resumeItem{Technologies Used: Next.js, React, PostgreSQL, OpenAI, Pinecone}
       \resumeItemListStart
           \resumeItem{Reduced job application processing time by ~50\% through automation and streamlined data entry.}
         \resumeItemListEnd
     

       \resumeProjectHeader
         {Instant Video Caption Generator (Jelly Up!)}{Aug 2024}
       
       \resumeProjectDetails{Backend video captioning pipeline using AI models.}
       \resumeItem{Technologies Used: Next.js, React, Docker, OpenCV, OpenAI Whisper}
       \resumeItemListStart
           \resumeItem{Developed a captioning backend that produced accurate captioned videos.}
          \resumeItem{Project placed 2nd at the Headstarter Hiring Hackathon.}
         \resumeItemListEnd
     

       \resumeProjectHeader
         {Globetrotter AI (Voice Activated Travel Assistant)}{Aug 2024}
       
       \resumeProjectDetails{Full‑stack voice‑activated travel assistant integrating multiple APIs.}
       \resumeItem{Technologies Used: Flask, Python, APIs}
       \resumeItemListStart
           \resumeItem{Designed and shipped the assistant and won 1st place at the Headstarter Hiring Hackathon.}
         \resumeItemListEnd
     

       \resumeProjectHeader
         {RAG 'Rate My Professor' Chat Application}{Aug 2024}
       
       \resumeProjectDetails{Real‑time chat app using vector search for professor reviews.}
       \resumeItem{Technologies Used: Next.js, TypeScript, Pinecone, OpenAI}
       \resumeItemListStart
           \resumeItem{Built realtime data fetching and vector search to improve response accuracy.}
         \resumeItemListEnd
     
     \resumeSubHeadingListEnd
%-----------TECHNICAL SKILLS-----------
\section{Skills}
\resumeFlexContent{Technical:}{Python, JavaScript / TypeScript, React (3 yrs), Next.js, Node.js, React Native, PostgreSQL, Supabase, Firebase, Docker, Pinecone, LangChain, OpenAI}
        \resumeFlexContent{Additional:}{Mobile app publishing (App Store), Algorithmic trading / quantitative strategies, UI/UX design, Agile, Leadership, Mentoring}
%-----------ADDITIONAL INFO-----------
\section{Additional Information}
\resumeFlexContent{Interests:}{Mentoring, Investing, Crypto, Basketball, Gaming, Traveling, Teaching}
        \resumeFlexContent{Hobbies:}{Piano, Guitar, Art}
        \resumeFlexContent{Languages:}{English (Native)}
        \resumeFlexContent{References:}{Available upon request}
\end{document}