\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{lmodern}  % Latin Modern fonts for better coverage
\usepackage[T1]{fontenc}  % Use T1 encoding for better font support
\usepackage{latexsym}
\usepackage{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{babel}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage[pdftex]{bookmark}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting - REDUCED SPACING
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-2pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}

\newcommand{\resumeFlexContent}[2]{
  \noindent\begin{minipage}[t]{0.2\textwidth}
    \textbf{#1}
  \end{minipage}%
  \hfill % This creates the space-between effect
  \begin{minipage}[t]{0.75\textwidth}
    \raggedright #2
  \end{minipage}\\[4pt]
}

% REDUCED SPACING in resumeSubheading
\newcommand{\resumeSubheading}[4]{\vspace{-4pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-5pt}}

% Modified to handle long technology lists with a comma-separated inline format
\newcommand{\resumeProjectHeading}[2]{\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & \small#2 \\
  \end{tabular*}\vspace{-5pt}}

\newcommand{\resumeProjectHeader}[2]{
  \vspace{-2pt}
  \item[]
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectDetails}[1]{
  \vspace{3pt}
  \begin{minipage}[t]{0.97\textwidth}
    \small #1
  \end{minipage}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% Set global paragraph spacing to minimum
\setlength{\parskip}{0pt}

% Set global paragraph spacing to minimum
\setlength{\parskip}{0pt}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setlength{\parskip}{0pt}
\begin{document}

\begin{center}
  \textbf{\Huge \scshape Itwela Ibomu} \\ \vspace{1pt}
  \small \href{mailto:iibomu@wgu.edu}{\underline{iibomu@wgu.edu}} $|$
  
  
  \href{https://linkedin.com/in/itwela}{\underline{linkedin.com/in/itwela}} $|$
  \href{https://github.com/itwela}{\underline{github.com/itwela}} $|$
  \href{https://itwela.dev}{\underline{itwela.dev}}
\end{center}
%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
           
             \resumeSubheading
               {Western Governors University (WGU) — Salt Lake City, UT}{}
               {B.S. in Software Engineering }{Estimated Graduation: }
               \resumeItemListStart
                 \resumeItem{Relevant Coursework: Data Structures \& Algorithms, Python, Front-End Web Development, JavaScript}
               \resumeItemListEnd
           
           \resumeSubHeadingListEnd
%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
           
             \resumeSubheading
               {Software Engineer}{}
               {Dope Marketing}{Jul 2025–Present}
               \resumeItemListStart
                 \resumeItem{Built internal AI platform used by 3 managers to automate account research and data analysis.}
          \resumeItem{Created APIs granting agents instant access to millions of housing and client records, cutting manual lookup time from hours to minutes.}
          \resumeItem{Enabled instant employee insights via CliftonStrengths API integration, improving decision speed for leadership teams.}
          \resumeItem{Delivered 3 production tools adopted by management, enhancing research efficiency across departments.}
               \resumeItemListEnd
           

             \resumeSubheading
               {Software Engineering Fellow}{}
               {Headstarter}{Jul 2024–Sep 2024}
               \resumeItemListStart
                 \resumeItem{Led a team of 3 to build CitySwipe, an AI vacation planner with 200 users and 50K+ impressions.}
          \resumeItem{Won 1st place out of 300+ teams in a nationwide hackathon for innovation and product execution.}
          \resumeItem{Shipped 5 AI web apps using Next.js, LangChain, and Supabase; scaled multiple to 200+ users.}
               \resumeItemListEnd
           

             \resumeSubheading
               {AI Engineer}{}
               {Dataforce}{Apr 2024–Jun 2024}
               \resumeItemListStart
                 \resumeItem{Reduced captioning error rates by 20\% across ~200 videos/day through workflow optimization.}
          \resumeItem{Improved data processing consistency and automated recurring QA checks for higher reliability.}
               \resumeItemListEnd
           

             \resumeSubheading
               {Software Intern}{}
               {J.P. Morgan (Forage)}{Dec 2023–Jan 2024}
               \resumeItemListStart
                 \resumeItem{Built real-time data visualization tool (<200ms updates) using the Perspective library.}
          \resumeItem{Gained exposure to enterprise-scale data systems and visualization workflows.}
               \resumeItemListEnd
           
           \resumeSubHeadingListEnd
%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
     
       \resumeProjectHeader
         {Lotus – AI Wellness App}{Sep 2025}
       
       \resumeProjectDetails{AI-powered React Native app generating articles, images, and audio for wellness content.}
       \resumeItem{Technologies Used: React Native, Replicate, OpenAI, Convex}
       \resumeItemListStart
           \resumeItem{Built multi-step AI pipeline with Convex workflow; reduced generation errors by 40\%.}
          \resumeItem{Achieved 40+ signups and 2 paying users with no active marketing.}
         \resumeItemListEnd
     

       \resumeProjectHeader
         {CitySwipe – AI Travel Planner}{Jul 2024–Present}
       
       \resumeProjectDetails{Personalized travel recommendations via LLM + vector search.}
       \resumeItem{Technologies Used: Next.js, LangChain, Pinecone, Supabase}
       \resumeItemListStart
           \resumeItem{50K impressions and 200 users; secured early investor interest.}
         \resumeItemListEnd
     

       \resumeProjectHeader
         {Job Tracker \& Analytics Dashboard}{Jan–Apr 2024}
       
       \resumeProjectDetails{Automated job tracking workflow, cutting completion time by 50\%.}
       \resumeItem{Technologies Used: Next.js, PostgreSQL, Supabase}
       
     

       \resumeProjectHeader
         {Jelly Up! – AI Caption Generator}{Aug 2024}
       
       \resumeProjectDetails{Automated subtitles with Whisper + OpenCV; judged 2nd place at Headstarter Hiring Hackathon.}
       \resumeItem{Technologies Used: Next.js, Whisper, Docker}
       
     

       \resumeProjectHeader
         {Globetrotter AI – Voice Travel Assistant}{Aug 2024}
       
       \resumeProjectDetails{Voice-activated travel planner integrating speech recognition and travel APIs.}
       \resumeItem{Technologies Used: Flask, Python, OpenAI}
       \resumeItemListStart
           \resumeItem{Won 1st place at Headstarter Hiring Hackathon.}
         \resumeItemListEnd
     
     \resumeSubHeadingListEnd
%-----------TECHNICAL SKILLS-----------
\section{Skills}
\resumeFlexContent{Technical:}{Python, JavaScript, TypeScript, React, Next.js, React Native, Node.js, Ruby on Rails, PostgreSQL, Supabase, Firebase, Docker, Pinecone, LangChain, OpenAI, Convex}
        \resumeFlexContent{Additional:}{UI/UX Design, Product Development, Agile, Leadership}
%-----------ADDITIONAL INFO-----------
\section{Additional Information}

        
        \resumeFlexContent{Languages:}{English (Native)}
        \resumeFlexContent{References:}{Available upon request}
\end{document}