\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{lmodern}  % Latin Modern fonts for better coverage
\usepackage[T1]{fontenc}  % Use T1 encoding for better font support
\usepackage{latexsym}
\usepackage{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{babel}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage[pdftex]{bookmark}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting - REDUCED SPACING
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-2pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}

\newcommand{\resumeFlexContent}[2]{
  \noindent\begin{minipage}[t]{0.2\textwidth}
    \textbf{#1}
  \end{minipage}%
  \hfill % This creates the space-between effect
  \begin{minipage}[t]{0.75\textwidth}
    \raggedright #2
  \end{minipage}\\[4pt]
}

% REDUCED SPACING in resumeSubheading
\newcommand{\resumeSubheading}[4]{\vspace{-4pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-5pt}}

% Modified to handle long technology lists with a comma-separated inline format
\newcommand{\resumeProjectHeading}[2]{\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & \small#2 \\
  \end{tabular*}\vspace{-5pt}}

\newcommand{\resumeProjectHeader}[2]{
  \vspace{-2pt}
  \item[]
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectDetails}[1]{
  \vspace{3pt}
  \begin{minipage}[t]{0.97\textwidth}
    \small #1
  \end{minipage}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% Set global paragraph spacing to minimum
\setlength{\parskip}{0pt}

% Set global paragraph spacing to minimum
\setlength{\parskip}{0pt}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setlength{\parskip}{0pt}
\begin{document}

\begin{center}
  \textbf{\Huge \scshape Itwela Ibomu} \\ \vspace{1pt}
  \small \href{mailto:Iibomu@wgu.edu}{\underline{Iibomu@wgu.edu}} $|$
  
  Salt Lake City, UT $|$
  \href{https://www.linkedin.com/in/itwela}{\underline{www.linkedin.com/in/itwela}} $|$
  \href{https://github.com/itwela}{\underline{github.com/itwela}} $|$
  \href{https://itwela.dev}{\underline{itwela.dev}}
\end{center}
%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
           
             \resumeSubheading
               {Western Governors University (WGU)}{Salt Lake City, UT}
               {Bachelor of Science in Software Engineering }{Estimated Graduation: Expected Dec 2025}
               \resumeItemListStart
                 \resumeItem{Relevant coursework: Data Structures \& Algorithms, Database Management, Software Design \& Architecture, Machine Learning Foundations.}
          \resumeItem{Developed strong foundations in mathematics, programming, data management, and application design.}
               \resumeItemListEnd
           
           \resumeSubHeadingListEnd
%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
           
             \resumeSubheading
               {Dope Marketing}{Minnesota}
               {Software Engineer}{Jul 2025 - Present}
               \resumeItemListStart
                 \resumeItem{Built an end-to-end AI Agent platform using React, Next.js, Ruby on Rails, TypeScript, OpenAI Agent SDK, Pinecone, and RAG services to assist account management workflows.}
          \resumeItem{Implemented secure user authentication, session management, and conversational interfaces enabling account teams to log in, hold conversations, and access a centralized knowledge base.}
          \resumeItem{Designed and maintained a production knowledge base pipeline: transcribed and processed call recordings (Fathom) into searchable embeddings, cleaned and transformed noisy transcription data, and indexed vectors in Pinecone for retrieval.}
          \resumeItem{Developed custom tools and connectors so agents could call internal APIs and third-party services (calendar, CRM, docs) to surface relevant, real-time information to users.}
          \resumeItem{Collaborated directly with the company owner and account teams; ran demos, collected feedback, and iterated on product features through weekly sprints to improve accuracy and adoption.}
               \resumeItemListEnd
           

             \resumeSubheading
               {Headstarter}{Long Island City, NY}
               {Software Engineering Fellow}{Jul 2024 – Sep 2024}
               \resumeItemListStart
                 \resumeItem{Built and deployed 5 AI-driven web applications using React (TypeScript), Next.js, Tailwind, Firebase, Supabase, Clerk, LangChain, Pinecone, Docker, and Vercel.}
          \resumeItem{Scaled multiple web apps to 200+ active users by iterating on user feedback and improving performance and UX.}
          \resumeItem{Led the development of 'CitySwipe' which secured early investment interest and won multiple hackathons.}
               \resumeItemListEnd
           

             \resumeSubheading
               {Dataforce}{Atlanta, GA}
               {AI Engineer}{Apr 2024 – Jun 2024}
               \resumeItemListStart
                 \resumeItem{Improved captioning pipeline efficiency by 20\% through workflow optimization and automation, increasing throughput and client satisfaction.}
          \resumeItem{Diagnosed and fixed recurring technical issues in production, reducing error rates and accelerating delivery timelines.}
          \resumeItem{Collaborated with cross-functional teams to refine requirements and ensure high-quality deliverables.}
               \resumeItemListEnd
           

             \resumeSubheading
               {Forage (J.P. Morgan Virtual Experience)}{Remote}
               {Software Engineering Virtual Intern}{Dec 2023 – Jan 2024}
               \resumeItemListStart
                 \resumeItem{Set up development environment and implemented live graph generation using JPMorgan Chase’s open-source Perspective library.}
          \resumeItem{Completed assigned tasks on time and demonstrated ability to work with financial-data visualization tooling.}
               \resumeItemListEnd
           
           \resumeSubHeadingListEnd
%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
     
       \resumeProjectHeader
         {Lotus (Voice \& Multimedia Article App)}{Released Sep 18, 2025}
       
       \resumeProjectDetails{React Native mobile app that generates multimedia articles (text, images, audio) by orchestrating multiple AI services. Includes step tracker, guided meditation, music library, and hydration reminders.}
       \resumeItem{Technologies Used: React Native, Replicate, React, Audio generation, Background audio, Offline caching}
       \resumeItemListStart
           \resumeItem{Built a multi-step generation pipeline that makes parallel calls to text, image, and audio generation models, post-processes results, and bundles them into a mobile article library.}
          \resumeItem{Implemented audio playback, offline caching, a step tracker, guided meditations, a music library, and water reminder features.}
          \resumeItem{Managed App Store submission and release process (App Store release: Sep 18, 2025).}
         \resumeItemListEnd
     

       \resumeProjectHeader
         {CitySwipe (AI Travel \& Vacation Planning)}{Jul 2024 – Present}
       
       \resumeProjectDetails{AI-powered vacation planning platform that recommends destinations, itineraries, and booking options using LLMs and vector search.}
       \resumeItem{Technologies Used: Next.js, React, Vercel, Supabase, Gemini, Pinecone, LangChain}
       \resumeItemListStart
           \resumeItem{Led product and engineering efforts; grew user base to 50+ active users and achieved thousands of social impressions.}
          \resumeItem{Secured early investment interest through strategic pitching and demonstrated product-market fit.}
         \resumeItemListEnd
     

       \resumeProjectHeader
         {Job Tracker \& Data Analysis Application}{Jan 2024 – Apr 2024}
       
       \resumeProjectDetails{Productivity tool to track job applications, automate workflows, and analyze application success metrics.}
       \resumeItem{Technologies Used: Next.js, React, Node.js, PostgreSQL, Supabase}
       \resumeItemListStart
           \resumeItem{Reduced average job application completion time by 50\% using automation and streamlined UI.}
          \resumeItem{Implemented reporting dashboards to monitor application progress and outcomes.}
         \resumeItemListEnd
     

       \resumeProjectHeader
         {RAG 'Rate My Professor' Chat Application}{Aug 2024}
       
       \resumeProjectDetails{Retrieval-Augmented Generation chat app that provides real-time professor ratings and reviews with vector search.}
       \resumeItem{Technologies Used: Next.js, TypeScript, Pinecone, OpenAI}
       \resumeItemListStart
           \resumeItem{Built real-time data fetching and vector search to improve accuracy and responsiveness of user queries.}
         \resumeItemListEnd
     

       \resumeProjectHeader
         {Instant Video Caption Generator (Jelly Up!)}{Aug 2024}
       
       \resumeProjectDetails{Automated video captioning system using OpenAI Whisper and OpenCV to produce accurate subtitles.}
       \resumeItem{Technologies Used: Next.js, React, Docker, OpenCV, OpenAI Whisper}
       \resumeItemListStart
           \resumeItem{Developed backend processing pipeline for video transcription and caption embedding; judged 2nd place at Headstarter Hiring Hackathon.}
         \resumeItemListEnd
     

       \resumeProjectHeader
         {Globetrotter AI (Voice-Activated Travel Assistant)}{Aug 2024}
       
       \resumeProjectDetails{Voice-activated AI assistant for travel planning integrating multiple travel APIs and voice recognition.}
       \resumeItem{Technologies Used: Flask, Python, REST APIs, OpenAI}
       \resumeItemListStart
           \resumeItem{Designed and implemented full-stack solution; won 1st place at Headstarter Hiring Hackathon for innovation and execution.}
         \resumeItemListEnd
     
     \resumeSubHeadingListEnd
%-----------TECHNICAL SKILLS-----------
\section{Skills}
\resumeFlexContent{Technical:}{Python, JavaScript (React, Next.js, Node.js, TypeScript), React Native, PostgreSQL, Supabase, Firebase, Docker, Pinecone, LangChain, OpenAI, OpenCV, Replicate, Ruby on Rails}
        \resumeFlexContent{Additional:}{UI/UX Design, Leadership, Teamwork, Agile methodologies, Product Development, Mentoring}
%-----------ADDITIONAL INFO-----------
\section{Additional Information}
\resumeFlexContent{Interests:}{Mentoring, Investing, Crypto, Basketball, Gaming, Traveling, Teaching Piano, Guitar, Digital art}
        
        \resumeFlexContent{Languages:}{English (Native)}
        \resumeFlexContent{References:}{Available upon request}
\end{document}